The globular cluster system of the Auriga simulations

### 2020-04-06 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction (of referee report)}
The following listing shows our reponse to the 3 paragraphs in the introduction
of the referee report.
\begin{enumerate}
\item We updated the abstract to clarify that we meant to describe what would
be needed for the environmental dependence of the formation and disruption of
bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
``The results of the paper clearly demonstrate that the technique of simulating
stellar clusters in cosmological hydrodynamical simulations by tagging stellar
particles based on their ages does not reproduce key properties of observed GC 
systems in the Milky Way and M31. However, the authors do not state this conclusion
anywhere''.

We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. Indeed, we do find that age-selected stellar particles do not 
reproduce key properties of observed GC systems in the Milky Way and M31. However,
our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. 
\end{enumerate}

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers instead of words.
\item We now first use the name of the physical quantities in the given example,
    followed by the symbolic representation.
\item TODO: parenthesis
\item Colloquial expressions have been rephrased.
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item TODO: add a paragraph in introduction to justify why we consider metallicity
and galactocentric radius.
\item TODO: justify age cut instead of using a more elaborate selection function.
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item TODO justify the modelling philosophy.
\item TODO: clarify why observational data has different numbers
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, etc). The simulations show a wide variety between properties of the Auriga
galaxies with little correlation between these different stellar length scales.
The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc.

\end{itemize}

### 2020-04-06 AurigaGCS.tex
Response to first point in introduction of referee report

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic globular cluster (GC) population. 
We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
This may imply that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic globular cluster (GC) population. 
We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We also find varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($r_{\text{gal}}$-[Fe/H]).
Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. The Auriga simulations would
require bound cluster formation efficiencies higher than ten percent for the 
metal-poor GC candidates, and those within the Solar radius should experience 
negligible destruction rates to be consistent with observations.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}
